An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-14 paper.tex
Proofed equipment section.

@@

\begin{itemize}
  \item A ForceLink R-Mill treadmill which has dual 6 degree of freedom force
    plates, independent belts for each foot, and motion capabilities (lateral,
    pitch).
  \item A 10 camera Motion Analysis motion capture system which includes Osprey
    cameras, the Cortex software (3.1.1.1290), and hardware for collecting
    analog and camera data simultaneously.
  \item National Instruments USB-6255 data acquisition unit.
  \item Four Sparkfun ADXL330 Triple Axis Accelerometer Breakout boards
    attached to the treadmill.
  \item Motek Medical’s D-Flow software (3.16.1 to 3.16.2) and visual display
    system.
\end{itemize}

The Cortex software delivers 3D marker trajectories from the cameras along with
data from force plates and analog sensors (EMG/Accelerometer) through a
National Instruments USB-6255 data acquisition unit. D-Flow is required to
collect data from any digital sensors and to control the treadmill's motion
(lateral, pitch, and belts). D-Flow can process the data in real time and/or
export data to file.

Our motion capture system's coordinate system is such that the X coordinate
points to the right, the Y coordinate points upwards, and the Z coordinate
follows from the right-hand-rule, i.e. points backwards with respect to a
person walking forward on the treadmill. The camera's coordinate system is
aligned to an origin point on treadmill's surface during camera calibration.
The same point is used as the origin of the ground reaction force measuring
system. Figure~\ref{fig:treadmill} shows the layout of the equiptment.

\begin{figure*}
  \centering
  \includegraphics{figures/treadmill.png}
  \caption{The treadmill, cameras, projection screen, and saftey rope. The
    direction of travel is in the $-z$ direction.}
  \label{fig:treadmill}
\end{figure*}

@@

\section*{Data Limitations}
%
The data is provided in good faith with great attention to detail. The
following list gives various notes and warnings about the data that should be
taken into account when making use of it.
%
\begin{itemize}
  \item Be sure to read the notes in each meta data file for details about
    possible anomalies in that particular trial.
  \item The subject identification number 0 stands for "no subject" and was
    used whenever data was collected from the system with no subject on the
    treadmill, for example during the trials that were intended to be used for
    inertial compensation purposes if the treadmill was moving. These trials
    play through the exact protocol as those with a human subject and the
    matching trials are indicated in the meta data. (TvdB: can the user tell
    which compensation file to use with which subject files?  By the date on
    the file?)
  \item Trials 1 and 2 were not recorded as part of this study. Those trial
    identification numbers were reserved for early data exploration from data
    collected in other studies.
  \item Trials 37, 38, and 39 do not exist. The numbers were accidentally
    skipped.
  \item Trials 9, 10, and 11 used a slightly different event definition where the
    calibration poses were not explicitly tagged by an event, yet the protocol
    was the identical to the following trials.
  \item During trials 9-15 we used wooden blocks to fix the treadmill to the
    concrete floor to eliminate the treadmill's lowest factory vibration mode
    (~5 hz). But these blocks seem to have corrupted the force plate
    measurements by imposing frictional stresses on the system. The force plate
    measurements should not be used from these trials, but the marker data is
    fine.
  \item We did not record unloaded compensation trials for trials 9-15.
    Regardless, they would be useless due to the previous point.
  \item Trials 6-8 use an early experimental protocol which divided the
    perturbation sections into three sections: longitudinal perturbations,
    lateral perturbations, and a combination of each. We then learned the
    treadmill had a low vibrational mode which significantly affects the force
    plate measurements. The force measurements during these trials are
    corrupted by this vibrational mode and should be used with caution or not
    at all.
  \item Trials 6-8 use a XX lower body marker set only.
  \item The ankle joint torques computed from subject 9's data in trials 25-27
    are abnormal and should be used with caution or not at all. We were not
    about to locate the source of the error, but it is likely related to the
    force calibration.
\end{itemize}

>>>>

% for nice units
\usepackage{siunitx}

@@

\begin{itemize}
  \item A R-Mill treadmill which has dual 6 degree of freedom force plates,
    independent belts for each foot, and lateral/pitch motion capabilities
    (Forcelink, Culemborg, Netherlands).
  \item A 10 Osprey camera motion capture system paired with the Cortex
    3.1.1.1290 software (Motion Analysis, Santa Rosa, CA, USA).
  \item USB-6255 data acquisition unit (National Instruments, Austin, Texas,
    USA).
  \item Four ADXL330 Triple Axis Accelerometer Breakout boards attached to the
    treadmill (Sparkfun, Niwot, Colorado, USA).
  \item D-Flow software (versions 3.16.1 to 3.16.2) and visual display system,
    (Motek Medical, Amsterdam, Netherlands).
\end{itemize}

The Cortex software delivers high accuracy 3D marker trajectories from the
cameras along with data from force plates and analog sensors
(EMG/Accelerometer) through a National Instruments USB-6255 data acquisition
unit. D-Flow is required to collect data from any digital sensors and to
control the treadmill's motion (lateral, pitch, and belts). D-Flow can process
the data in real time and/or export data to file.

Our motion capture system's coordinate system is such that the X coordinate
points to the right, the Y coordinate points upwards, and the Z coordinate
follows from the right-hand-rule, i.e. points backwards with respect to the
walking direction. The camera's coordinate system is aligned to an origin point
on treadmill's surface during camera calibration. The same point is used as the
origin of the ground reaction force measuring system.
Figure~\ref{fig:treadmill} shows the layout of the equipment.

Early on, we discovered that the factory setup of the R-Link treadmill had a
vibration mode as low as 5 Hz that is detectable in the force measurements,
likely due to the flexible undercarriage and pitch motion mechanism. Trials 6-8
are affected by this vibration mode. During trials 9-15 the treadmill was
stabilized with wooden blocks. During, the remaining trials the treadmill was
stabilized with metal supports. See the Data Limitations Section for more
details.

The acceleration of the treadmill was measured during each trial by four
ADXL330 accelerometers placed at the four corners of the machine. These
accelerometers were intended to provide information for inertial compensation
purposes when the treadmill moved laterally, but are extraneous for trials
greater than 8 due to the treadmill being stabilized.
%
\begin{figure*}
  \centering
  \includegraphics{figures/treadmill.png}
  \caption{The treadmill with coordinate system, cameras (circled in orange),
    projection screen, and safety rope. The direction of travel is in the $-z$
    direction.}
  \label{fig:treadmill}
\end{figure*}

@@

\section*{Data Limitations}
%
The data is provided in good faith with great attention to detail. The
following list gives various notes and warnings about the data that should be
taken into account when making use of it.
%
\begin{itemize}
  \item Be sure to read the notes in each meta data file for details about
    possible anomalies in that particular trial.
  \item The subject identification number 0 stands for "no subject" and was
    used whenever data was collected from the system with no subject on the
    treadmill, for example during the trials that were intended to be used for
    inertial compensation purposes if the treadmill was moving. These trials
    play through the exact protocol as those with a human subject and the
    matching trials are indicated in the meta data. (TvdB: can the user tell
    which compensation file to use with which subject files?  By the date on
    the file?)
  \item Trials 1 and 2 were not recorded as part of this study. Those trial
    identification numbers were reserved for early data exploration from data
    collected in other studies.
  \item Trials 37, 38, and 39 do not exist. The numbers were accidentally
    skipped.
  \item  Trials 6-15 force measurements are affected by this and should be not
    be used. We include the trials because the kinematic data is valid and
    trials 6-8 include lateral perturbations in addition to the longitudinal.
  \item Trials 9, 10, and 11 used a slightly different event definition where the
    calibration poses were not explicitly tagged by an event, yet the protocol
    was the identical to the following trials.
  \item During trials 9-15 we used wooden blocks to fix the treadmill to the
    concrete floor to eliminate the treadmill's lowest factory vibration mode
    (~5 hz). But these blocks seem to have corrupted the force plate
    measurements by imposing frictional stresses on the system. The force plate
    measurements should not be used from these trials, but the marker data is
    fine.
  \item We did not record unloaded compensation trials for trials 9-15.
    Regardless, they would be useless due to the previous point.
  \item Trials 6-8 use an early experimental protocol which divided the
    perturbation sections into three sections: longitudinal perturbations,
    lateral perturbations, and a combination of each. We then learned the
    treadmill had a low vibrational mode which significantly affects the force
    plate measurements. The force measurements during these trials are
    corrupted by this vibrational mode and should be used with caution or not
    at all.
  \item Trials 6-8 use a XX lower body marker set only.
  \item The ankle joint torques computed from subject 9's data in trials 25-27
    are abnormal and should be used with caution or not at all. We were not
    about to locate the source of the error, but it is likely related to the
    force calibration.
\end{itemize}
